Secure Composition of Robust and Optimising Compilers

### 2023-07-11 popl/main.tex
fixes

\begin{theorem}[Compiler $\ccmsscct$ is secure with respect to \gls{scct}]\label{thm:ccall:rtp:msscct}
  $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$ \Coqed
\end{theorem}
\begin{proof}
	From \Thmref{thm:ccscct:rtp:scct}, we have that any LTMS program \src{p} gets compiled into a L program \trg{p} that is also TMS.
	Then, from \Thmref{thm:cccfccdce:rtp:ms} we have that \trg{p} gets compilet to a program ?? that is also SMS, assuming it was SMS to begin with.
	Since TMS + SMS = MS, ?? is MS.
	?? gets optimised by the optimisation passes and its optimisation is ???, which is still MS.
	Finally, \Thmref{thm:ccab:rtp:ms} ensures that ??? gets compiled into ????, which is CCT assuming that the original program was CCT to begin with.
  % \MKin{%
  %   \textbackslash Thmref or \textbackslash Cref?
  % }
% Unfold the definition of $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$.
% So, let $\pi\in\mssafe\cap\scctsafe$, $\src{\progvar}$ such that $\rsat{\src{\progvar}}{\pi}$ and let $\obj{\contextvar},\obj{\runtimetermvar}$ with $\progstepto{\prog[\obj]{\obj{\contextvar}}{\left(\cc{\Ltms}{\Lscct}(\src{\progvar})\right)}}{\obj{\runtimetermvar}}{\obj{\trace}}$.
% What is left to show is $\scctfilterLscct[\emptyset]{\obj{\trace}}\in\pi$.
% Let $\irl{\progvar}=\cc{\Ltms}{\Ltrg}\circ\cc{\Ltrg}{\Lms}\circ\cc[\gls{cf}]{\Lms}{\Lms}\circ\cc[\gls{dce}]{\Lms}{\Lms}(\src{\progvar})$ such that $\cc{\Lms}{\Lscct}(\irl{\progvar})=\cc{\Ltms}{\Lscct}(\src{\progvar})$.
% Note that $\pi\in\scctsafe$, so apply \Thmref{thm:ccscct:rtp:scct}
\end{proof}

>>>>

\begin{theorem}[Compiler $\ccmsscct$ is secure with respect to \gls{scct}]\label{thm:ccall:rtp:msscct}
  $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$ \Coqed
\end{theorem}
\begin{proof}
	From \Thmref{thm:ccscct:rtp:scct}, we have that any LTMS program $\src{p}$ gets compiled into a L program $\trg{p}$ that is also TMS.
	Then, from \Thmref{thm:cccfccdce:rtp:ms} we have that $\trg{p}$ gets compilet to a program ?? that is also SMS, assuming it was SMS to begin with.
	Since TMS + SMS = MS, ?? is MS.
	?? gets optimised by the optimisation passes and its optimisation is ???, which is still MS.
	Finally, \Thmref{thm:ccab:rtp:ms} ensures that ??? gets compiled into ????, which is CCT assuming that the original program was CCT to begin with.
  % \MKin{%
  %   \textbackslash Thmref or \textbackslash Cref?
  % }
% Unfold the definition of $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$.
% So, let $\pi\in\mssafe\cap\scctsafe$, $\src{\progvar}$ such that $\rsat{\src{\progvar}}{\pi}$ and let $\obj{\contextvar},\obj{\runtimetermvar}$ with $\progstepto{\prog[\obj]{\obj{\contextvar}}{\left(\cc{\Ltms}{\Lscct}(\src{\progvar})\right)}}{\obj{\runtimetermvar}}{\obj{\trace}}$.
% What is left to show is $\scctfilterLscct[\emptyset]{\obj{\trace}}\in\pi$.
% Let $\irl{\progvar}=\cc{\Ltms}{\Ltrg}\circ\cc{\Ltrg}{\Lms}\circ\cc[\gls{cf}]{\Lms}{\Lms}\circ\cc[\gls{dce}]{\Lms}{\Lms}(\src{\progvar})$ such that $\cc{\Lms}{\Lscct}(\irl{\progvar})=\cc{\Ltms}{\Lscct}(\src{\progvar})$.
% Note that $\pi\in\scctsafe$, so apply \Thmref{thm:ccscct:rtp:scct}
\end{proof}
